

## Estimating the incubation period of a simulated Ebola outbreak

#### Note: compiling this document

This is a rmarkdown document.
Compile it using [*knitr*](http://yihui.name/knitr/) (google: *knitr* for more information).
Use `knit2html(...)` to generate a html report.



#### Incubation period

In the following, we use a simulated Ebola outbreak linelist to illustrate how to estimate the empirical distribution of the incubation time (delay between exposure and symptom onset).


We first load the data:

```{r}
library(outbreaks)
dat <- ebola.sim$linelist
```

We compute the incubation period and ensure that the result is `numeric`:
```{r, incub}
incub <- dat$date.of.onset - dat$date.of.infection
head(incub)
length(incub)
summary(incub)
incub <- as.numeric(incub)
summary(incub)
```

We remove the missing values, compute the mean and variance:
```{r, removeNA}
sum(is.na(incub))
incub <- incub[!is.na(incub)]
mean(incub)
var(incub)
```

Get the 95 percentile:
```{r, perc}
t <- quantile(incub, .95)
t
```

Quarantine should last for at least **`r t` days**.

Plot using basic graphics:
```{r, plot}
hist(incub, col="grey", border="white", xlab = "Days to show symptoms", main = "Distribution of incubation period")
abline(v = t, col = "red", lty = 2)
```

Version using *ggplot2*:

```{r, ggplot}
ggplot(data.frame(incubation = incub), aes(x=incub)) + 
  geom_histogram() +
  labs("Days to show symptoms", main = "Distribution of incubation period")
```

